\MCnote{Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Vehicle Platoons on Air Highways}

### 2016-11-18 docs/AIAA 2016 highway platooning/main.tex
minor changes to revision
added AIAA paper revision
second revision of UTM paper

%\newcommand{\MCnote}{\todo[size=\footnotesize,author=MC,color=cyan]}
\usepackage{cite}
\newcommand{\MCnote}{\textcolor{red}}

@@

\author{Mo Chen, Qie Hu, Jaime F. Fisac, Kene Akametalu, Casey Mackin, Claire J. Tomlin}
\title{\MCnote{Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Vehicle Platoons on Air Highways}}

\abstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations. As a result, unmanned aerial systems traffic management is needed to ensure the safety and \MCnote{goal satisfaction} of potentially thousands of UAVs flying simultaneously. Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers is unrestricted. In this paper, platoons of UAVs flying on air highways is proposed to impose an airspace structure that allows for tractable analysis. For the air highway placement problem, the fast marching method is used to produce a sequence of air highways that minimizes the cost of flying from an origin to any destination. The placement of air highways can be updated in real-time to accommodate sudden airspace changes. Within platoons traveling on air highways, each vehicle is modeled as a hybrid system. Using Hamilton-Jacobi reachability, safety and \MCnote{goal satisfaction} are guaranteed for all mode transitions. For a single altitude range, the proposed approach guarantees safety for one safety breach per vehicle; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges. Safety and \MCnote{goal satisfaction} are demonstrated through simulations of three scenarios.}

>>>>

%\newcommand{\MCnote}{\todo[size=\footnotesize,author=MC,color=cyan]}
\usepackage{cite}
%\newcommand{\MCnote}[1]{\textcolor{red}{\textbf{#1}}}
\newcommand{\MCnote}{\textcolor{black}}

@@

\author{Mo Chen\thanks{PhD Candidate, Department of Electrical Engineering and Computer Sciences}, Qie Hu\thanksibid{1}, Jaime F. Fisac\thanksibid{1}, Kene Akametalu\thanksibid{1}, Casey Mackin\thanks{PhD Student, Department of Electrical Engineering and Computer Sciences}, Claire J. Tomlin\thanks{Professor, Department of Electrical Engineering and Computer Sciences}\\\textit{University of California, Berkeley}}
\title{\MCnote{Reachability-Based Safety and Goal Satisfaction of Unmanned Aerial Vehicle Platoons on Air Highways}}

\AIAAabstract{Recently, there has been immense interest in using unmanned aerial vehicles (UAVs) for civilian operations. As a result, unmanned aerial systems traffic management is needed to ensure the safety and \MCnote{goal satisfaction} of potentially thousands of UAVs flying simultaneously. Currently, the analysis of large multi-agent systems cannot tractably provide these guarantees if the agents' set of maneuvers is unrestricted. In this paper, platoons of UAVs flying on air highways is proposed to impose an airspace structure that allows for tractable analysis. For the air highway placement problem, the fast marching method is used to produce a sequence of air highways that minimizes the cost of flying from an origin to any destination. The placement of air highways can be updated in real-time to accommodate sudden airspace changes. Within platoons traveling on air highways, each vehicle is modeled as a hybrid system. Using Hamilton-Jacobi reachability, safety and \MCnote{goal satisfaction} are guaranteed for all mode transitions. For a single altitude range, the proposed approach guarantees safety for one safety breach per vehicle; in the unlikely event of multiple safety breaches, safety can be guaranteed over multiple altitude ranges. We demonstrate the platooning concept through simulations of three representative scenarios.}

### 2016-11-18 docs/AIAA 2016 highway platooning/plat_sim.tex
finished editing
second revision of UTM paper

As the intruder $\veh{5}$ (yellow) continues to disregard other vehicles, the followers of the platoon also get near the respective boundaries of their safety BRSs with respect to the intruder. This occurs at $t=13.9$, where the platoon ``makes room'' for the intruder to pass by to avoid collisions; all vehicles deviate from their intended path, which is to follow the platoon leader or the highway.

@@

    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:in_140}
        \includegraphics[width=\columnwidth]{fig/in_140}
        \caption{Safety controllers cause vehicles to spread out to ``make room'' for the intruder to pass.}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:in_200}
        \includegraphics[width=\columnwidth]{fig/in_200}
        \caption{After danger has passed, the platoon resumes normal operation.}
    \end{subfigure}   
    \caption{A simulation showing how a platoon of four vehicles react to an intruder. \label{fig:in}}
\end{figure}

>>>>

As the intruder $\veh{5}$ (yellow) continues to disregard other vehicles, the followers of the platoon also get near the respective boundaries of their safety BRSs with respect to the intruder. This occurs at $t=13.9$, where the platoon ``makes room'' for the intruder to pass by to avoid collisions; all vehicles deviate from their intended path, which is to follow the platoon leader or the highway. \MCnote{Note that in this case, we have assumed that the platoon does not move as a unit in response to an intruder to show more interesting behavior.}

@@

    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:in_140}
        \includegraphics[width=\columnwidth]{fig/in_140}
        \caption{Safety controllers cause vehicles to spread out to ``make room'' for the intruder to pass.}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\columnwidth} \label{subfig:in_200}
        \includegraphics[width=\columnwidth]{fig/in_200}
        \caption{After danger has passed, the platoon resumes normal operation.}
    \end{subfigure}   
    \caption{A simulation showing how a platoon of four vehicles reacts to an intruder. \label{fig:in}}
\end{figure}
